Time and space specifications for stencils

### 2016-06-15 paper.tex
tweak syntax in inference descriptions

\begin{definition}[Constant translations]
An indexing expression $e$ is a \emph{constant translation} if,
for a base induction variable $i$, then $e \equiv i + a$ or $e \equiv i - a$
where $a$ is a constant. The relation $\equiv$ identifies terms
up-to commutativity of $+$ and the inverse
relation of $+$ and $-$ (\eg{}, $(-b) + i \equiv i - b$).
In the following, we classify constant translation expressions
using the predicate $\textsf{trans}$.
\end{definition}

@@

\dnote{Might want to do 'stencil' (gather) and 'mould' (scatter)
  patterns separately}
\begin{align*}
\begin{array}{lll}
\interp{e_1 = e_2}    & = \interp{e_2} \\
\interp{e_1 e_2}      & = \interp{e_1} \cup \interp{e_2} \\
\interp{a(\tilde{e})} & = \{e | e \in \tilde{e}, \textsf{trans}(e)\} & \textit{where each $e \in
                                          \tilde{e}$ is a constant or constant translation}
\end{array}
\end{align*}

@@

The reserved dimension \dimId{t}

>>>>

\begin{definition}[Neighbourhood indices]
An array subscript $e$ is a \emph{neighbourhood index} if,
for an induction variable $i$, then $e \equiv i + a$ or $e \equiv i - a$
where $a$ is a constant. The relation $\equiv$ identifies terms
up-to commutativity of $+$ and the inverse
relation of $+$ and $-$ (\eg{}, $(-b) + i \equiv i - b$).
In the following, we classify neighbourhood indices 
using the predicate $\textsf{neigh}$.
\end{definition}

@@

\dnote{Might want to do 'stencil' (gather) and 'mould' (scatter)
  patterns separately}
\begin{align*}
\begin{array}{lll}
\interp{e_1 = e_2}    & = \interp{e_2} \\
\interp{e_1 e_2}      & = \interp{e_1} \cup \interp{e_2} \\
\interp{a(\tilde{e})} & = \{e | e \in \tilde{e}, \textsf{neigh}(e)\} & \textit{where each $e \in
                                          \tilde{e}$ is a constant or constant translation}
\end{array}
\end{align*}

@@

\begin{itemize}
\item Extract from syntax finite map of variables
to relative-index verctors representing the contributing
array subscritps
\end{itemize}
